Verifying Demonstrations

### 2020-07-03 paper/DB-Schnorr-UWB.tex
Changes some equations to display, fixes bugs in eqns

    \vdots
    &
    &
    \\[-1em]

@@

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{m^n}\), where \(m\) is as in 
  \cref{DB-Schnorr-UWB}.
\end{theorem}

\begin{proof}
  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
  cannot learn anything by observation.
  This leaves the adversary with two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, receiving the challenge first would taint the 
    session (\cref{TaintedMF});
  \item guess the response.
  \end{enumerate*}
  The first option yields success with probability \(\frac{1}{m}\), since the 
  choice is uniformly distributed.
  The second option yields success with probability \(\frac{1}{q}\): since the 
  response~\(s_i\) depends on \(\rho\), which is uniformly distributed in 
  \(\ZZ_q\), it follows that \(s_i\) is also uniformly distributed in 
  \(\ZZ_q\).

  Since \(m \leq q\), the best strategy is to guess which challenge the 
  verifier will use.
  Thus, the total success probability is \(\frac{1}{m^n}\).
\end{proof}

@@

\begin{theorem}[\acs*{DBTF} resistance]
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \left(\frac{2}{m}\right)^n\).
\end{theorem}

\begin{proof}
  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
  with probability~\(p_{\adv}\) non-negligibly better than guessing (\(p_{\adv} 
  = \frac{1}{m}+\epsilon, \epsilon\) non-negligible), without tainting the 
  session (\cref{TaintedTF}) and leaking the secret~\(\alpha\).
  Say that \(\adv\) has successfully authenticated with the prover's help and 
  \(\S\) is given \(\adv\)'s state.

  Now \(\S\) will use \(\adv\) in a simulation.
  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge different from before.
  Since \(\adv\) cannot perform a relay to the prover without tainting the 
  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
  provided by the prover must be independent from the chosen challenge.
  Now \(\adv\) will again provide a correct response with 
  probability~\(p_{\adv}\).

  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
  \(m p_{\adv}\) responses.
  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
  correct responses and, thus, \(p_{\S} = 1\) for any successive 
  authentication.
  This would also make \(p_{\adv} = 1\).
  This contradicts that the secret is not leaked.
  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
  secret leaks.
\end{proof}

@@

\begin{theorem}[\acs*{DBDH}/\acs*{DBDF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\).
\end{theorem}

\begin{proof}
  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
  \(R' = R\) to not interfere.

  The verifier will choose \(c_1, \dotsc, c_k\).
  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
  is his \enquote{private key}\footnote{%
    In Schnorr's original protocol this was called the private key.
    But in our general use, it's the discrete logarithm for which the prover 
    wants to prove knowledge.
  }.
  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
  c_i \alpha'\), where \(\alpha'\) is the adversary's \enquote{private key}.
  If the adversary didn't choose \(R'\), he can only guess the values for 
  \(s_i'\).

  Now the adversary has two options:
  to \(\Commit\) to a response or to \(\Prompt\) the honest prover to respond.

  If the adversary \(\Commit\)s:
  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute \(s_i 
  = \rho' - c_i \alpha'\) for all \(i\).
  Now, the adversary must commit to one \(s_i\) before seeing the verifier's 
  choice \(j\).
  The probability of committing to the right one is \(\frac{1}{m}\).
  If the adversary didn't choose \(R'\) and consequently doesn't know \(\rho\), 
  the probability of success is \(\frac{1}{q}\) --- since he must guess 
  \(\rho\) (\(\frac{1}{q}\)) and then guess the challenge (\(\frac{1}{m}\)) he 
  might just as well guess the final outcome (\(\frac{1}{q}\)).
  By design, \(m \leq q\), so \(\frac{1}{m} \geq \frac{1}{q}\).
  The success of committing is \(\frac{1}{m}\).

  If the adversary \(\Prompt\)s:
  The verifier will check that \(R' = g^{s_i} A'^{c_i}\), where \(A'\) is the 
  \enquote{public key}\footnote{%
    In Schnorr's original protocol this was a public key.
    In our more general use, it is the value for which the adversary wants to 
    prove knowledge of a discrete logarithm.
  } of the adversary.
  Now, \(g^{s_i} A'^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = g^{\rho 
  - c_i \alpha + c_i \alpha'}\).
  If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 
  accept if \(\alpha = \alpha'\), the probability for which is 
  \(\frac{1}{q^2}\).
  If \(R' = g^{\rho'}\), chosen by the adversary, then the verifier accepts 
  with probability \(\Pr[\rho' - c_i \alpha' = \rho - c_i' \alpha] = 
  \frac{1}{q}\).

  Obviously, the better strategy for the adversary is to choose \(R' = 
  g^{\rho'}\).
  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
  \(\Prompt\) (\ac{DBDH}).
  We thus have that
  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\),
  which concludes the proof.
\end{proof}

>>>>

    \(\vdots\)
    &
    &
    \\[-1em]

@@

\begin{restatable}[\acs*{DBMF} resistance]{theorem}{UWBMFresistance}
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{m^n}\), where \(m\) is as in 
  \cref{DB-Schnorr-UWB}.
\end{restatable}

The proof is found in \cref{ProofUWBMFresistance}.

@@

\begin{restatable}[\acs*{DBTF} resistance]{theorem}{UWBTFresistance}
  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
  \(\S\) an algorithm with runtime \(t_{\S}\).
  If the verifier's challenges are uniformly drawn, then 
  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \left(\frac{2}{m}\right)^n\).
\end{restatable}

The proof is found in \cref{ProofUWBTFresistance}.

@@

\begin{restatable}[\acs*{DBDH}/\acs*{DBDF} 
  resistance]{theorem}{UWBDFresistance}
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\).
\end{restatable}

The proof is found in \cref{ProofUWBDFresistance}.
